Extended Data

### 2022-02-03 doc/manuscript/Dow_manuscript_Nature.Rmd
Update Dow_manuscript_Nature.Rmd
@camerondow35 , I added a bit back here to make sure the paragraph is setting up why our study is unique. Feel free to tweak.

While responses of leaf phenology and seasonal _NEE_ to warming spring temperatures have been documented[@jeong_phenology_2011; @keenan_net_2014; @buermann_widespread_2018; @ibanez_forecasting_2010; @menzel_european_2006; @menzel_growing_1999;@finzi_carbon_2020], little is known about how the longest-lived component of fixed C in trees, the woody stem growth, is responding to warming spring temperatures. 
This uncertainty has led to  a surge in recent studies documenting the climate sensitivity of stem growth timing and its link to annual growth[@dorangeville_peak_2021; @etzold_number_2022; @tumajer_limitation_2022; @zweifel_why_2021].

>>>>

While responses of leaf phenology and seasonal _NEE_ to warming spring temperatures have been documented[@jeong_phenology_2011; @keenan_net_2014; @buermann_widespread_2018; @ibanez_forecasting_2010; @menzel_european_2006; @menzel_growing_1999;@finzi_carbon_2020], little is known about how the longest-lived component of fixed C in trees, the woody stem growth, is responding to warming spring temperatures. 
This uncertainty has led to  a surge in recent studies documenting the climate sensitivity of stem growth timing and its link to annual growth[@dorangeville_peak_2021; @etzold_number_2022; @tumajer_limitation_2022; @zweifel_why_2021]; however, the role of spring temperatures in shaping the timing of growth remains unclear.
